\cvsection{Experience}
\begin{cventries}
  \cventry
    {Software Engineer}
    {Sigma Computing}
    {San Francisco, CA}
    {September 2024}
    {
      \begin{cvitems}
        \item {Constructed automated pipeline to create templates for \textbf{Kubernetes} jobs.}
        \item {Led small team in quickly iterating on an MVP internal link shortening service for the company hackathon.}
        \item {Setup cost-saving measures for CI/CD across entire tech stack.}
        \item {Used in Kubernetes clusters spanning 7 regions.}
      \end{cvitems}
    }
  % \cventry
  %   {Software Engineer Intern}
  %   {Sigma Computing}
  %   {San Francisco, CA}
  %   {June 2023 - September 2023}
  %   {
  %     \begin{cvitems}
  %       \item {Constructed automated pipeline to create templates for \textbf{Kubernetes} jobs.}
  %       \item {Led small team in quickly iterating on an MVP internal link shortening service for the company hackathon.}
  %       \item {Projects could save upwards to \$50,000/year in company expenses.}
  %       \item {Used in Kubernetes clusters spanning 7 regions.}
  %     \end{cvitems}
  %   }
  % \cventry
  %   {Undergraduate Researcher}
  %   {CSE Department at UC San Diego}
  %   {La Jolla, CA}
  %   {January 2022 - April 2022}
  %   {
  %     \begin{cvitems}
  %       \item {Researching methods of optimization of \href{https://github.com/google/deepvariant}{DeepVariant}, a convolutional neural network.}
  %       \item {Found multiple hot-paths critical for optimization on pipeline, used for cancer genomics.}
  %       \item {Presented findings to Micron and laboratory team.}
  %     \end{cvitems}
  %   }
  \cventry
    {Systems Engineer Intern}
    {ServiceNow}
    {San Diego, CA}
    {June 2021 - September 2021}
    {
      \begin{cvitems}
        \item {Constructed method to instantiate Azure VM images directly from centOS Kickstart file using \textbf{Packer} and \textbf{VMWare vSphere}.}
        \item {Saved upwards of 10 engineer workhours per run, with a projected total of 50 engineer workours per year.}
        \item {Worked in \textbf{GitLab CI} to allow for templating any image for Azure-based infrastructure.}
        \item {Used by over 500 Azure VM's running in lab and production environments.}
      \end{cvitems}
    }
  \cventry
  {Project Manager \& Automation Developer}
  {ACM @ UCSD}
  {La Jolla, CA}
  {May 2020 - May 2022}
  {
    \begin{cvitems}
      \item {Refactored and documented technology stack of all internal tooling using \textbf{Ansible}, \textbf{Vagrant} and \textbf{Terraform}, available at the GitHub repo \href{https://github.com/acmucsd/tech-stack}{tech-stack}.}
      \item {Internal tooling includes Discord bot, organization membership portal, password manager and workshop livestreaming platform.}
      \item {Leading development of organization \href{https://github.com/acmucsd/membership-portal-ui}{membership portal} using \textbf{React}, \textbf{TypeScript} and \textbf{PostgreSQL}.}
    \end{cvitems}
  }
  \cventry
    {Software Developer}
    {Digital Sky}
    {Bucharest, Romania}
    {January 2020 - Present}
    {
      \begin{cvitems}
        \item {Managed \textbf{PostgreSQL} databases and client-oriented software for television and satellite broadcasting company.}
        \item {Provisioned and managed 10 bare-metal servers using IaC tools such as \textbf{Ansible}, \textbf{Terraform} and \textbf{Digital Rebar}.}
        \item {Migrated 5 self-hosted instances of email servers and managed records such as \textbf{SPF}, \textbf{DKIM} and \textbf{DMARC}. Used by over 100+ employees.}
        \item {Configured self-hosted nameservers for 20 domains hosted by the company.}
      \end{cvitems}
    }
%   \cventry
%     {Television Broadcasting Intern}
%     {Realitatea TV}
%     {Bucharest, Romania}
%     {July 2018 - August 2018}
%     {
%       \begin{cvitems}
%         \item {Supervised and assigned duties to engineers engaged in technical control and production of radio and television programs.}
%         \item {Directed camera and video staff concerning shading and composition.}
%         \item {Managed the technical aspects and the program details of 3 prime-time live broadcasts of high-profile events.}
%         \item {Revised broadcast schedules of late-night public debate shows.}
%       \end{cvitems}
%     }
\end{cventries}
