\cvsection{Projects}

\begin{cventries}
  \cventry
    {HTML, Handlebars, Express, WebSockets}
    {BubbleChat - Real-Time Chat Application}
    {\href{https://github.com/StormFireFox1/BubbleChat}{GitHub}}
    {July 2018 - August 2018}
    {
      \begin{cvitems}
        \item {Co-created chat application that matches participants based on selected interests, or ``tags''.}
        \item {Express and WebSockets backend designed to allow for dynamic expansion of chatrooms.}
        \item {Application designed to create a fun and fast-paced socializing experience.}
        \item {Won Second-Best Overall, Best Backend prize at Stanford Pre-Collegiate Summer Institutes, Web Technologies Courses.}
      \end{cvitems}
    }
  \cventry
    {C++}
    {Probleme-Info-11G - Competitive Programming Problems Repository}
    {\href{https://github.com/StormFireFox1/Probleme-Info-11G}{GitHub}}
    {September 2017 - June 2019}
    {
      \begin{cvitems}
        \item {GitHub repository with 200 exercises from 2 Romanian competitive programming websites, as well as Codeforces.}
        \item {Served as a reference for tutoring lessons regarding complex algorithms such as dynamic programming, backtracking and pathfinding algorithms.}
      \end{cvitems}
    }
  \cventry
    {Java, Go, MongoDB}
    {VianuEdu - Educational Software}
    {\href{https://github.com/CNITV/VianuEdu}{GitHub}}
    {October 2017 - June 2018}
    {
      \begin{cvitems}
        \item {Co-created software capable of administering homework, as well as tests, used by over 100 students.}
        \item {Server written in \textbf{Go} with ease of deployment in mind; simple binary and shell scripts provided for easy configuration and adoption in educational system.}
        \item {Server additionally designed with safety checks to prevent violations of academic integrity.}
        \item {Used \textbf{Swift UI} for cross-platform GUI, designed with performance in mind to run on most low-end PCs, to allow for accessibility of educational material.}
        \item {Leveraged MongoDB as scalable database for ease of change in database schema in the future.}
      \end{cvitems}
    }
\end{cventries}
